An Open Repository of Real-Time COVID-19 Indicators

### 2021-09-16 indicators/paper/responses-to-reviews.tex

\begin{quote}
  Even from a nowcasting perspective, comparisons are all benchmarked against
  cases which are observable in real-time.
\end{quote}
TODO

\begin{quote}
  The strength of observed correlations change (non-monotonically) over time,
  and the implications of this are not discussed.
\end{quote}
While it is difficult to fully explain the changes in correlation---they are
likely due to a variety of changes in reporting practices, health-seeking
behavior, survey response patterns, and so on---one key point is that the
strength of the correlation depends on the overall differences between counties.
That is, if counties have very similar COVID case rates, it is difficult to
achieve a high Spearman correlation between case rates and signals, because
getting the rank correct is difficult. If counties have widely varying COVID
case rates, a signal that provides information about cases will be able to
achieve a higher Spearman correlation.

We have slightly expanded our discussion of Figure 2 to make this point, though
we have tried to keep the discussion brief so as not to sidetrack the main
discussion of the manuscript.

\begin{quote}
  Signal strength is compared only to cases (rather than downstream outcomes
  like hospitalization or death).
\end{quote}
We have extended the Supplementary Information to include more detailed
comparisons between our signals and reported COVID hospitalizations, including
comparisons of correlations. These show broadly similar results as the COVID
case analyses. Section 2.B now points to the Supplement for interested readers
to examine these analyses.

### 2021-09-16 indicators/paper/responses-to-reviews.tex

TODO any additional changes?

\begin{quote}
  The main value of the data discussed in the paper seems to focus on its
  potential utility in forecasting, which guides the main comparisons to
  observed case burden and primary outcome of ``signal value'' in results and in
  the appendix. However, there are a number of important limitations to the
  results presented that impede this message.

  Most concrete results on this point seem to be presented in another paper.
  Correlations in the paper are focused on current case burden (signal vs. cases
  both at time t), rather than prediction for forecasts.
\end{quote}
TODO

\begin{quote}
  Even from a nowcasting perspective, comparisons are all benchmarked against
  cases which are observable in real-time.
\end{quote}
We have extended the analysis to include comparisons against hospitalizations as
well; see below.

But it is worth emphasizing that cases are not actually observable in real time.
Case reporting typically occurs with lag; lag was often high early in the
pandemic when testing was limited and health departments were struggling to
scale up reporting systems, so case reports for a particular date may not have
been available until several days or a week later. This gradually changed until
most states reported cases daily---though these reports were still subject to
lag and referred to cases that may have been diagnosed several days earlier.
Now, some states have returned to a weekly reporting schedule, so case reports
only become available once a week, and so cases may take up to seven days to be
reported.

When our correlation analyses show a high correlation between a signal and case
reports on a specific date, that signal may have been available several days
before the case reports were, depending on the time this occurred during the
pandemic and the state's reporting practices. We have expanded Section 2.B to
make this point clearer.

### 2021-09-16 indicators/paper/paper.tex
Point out that case lag means correlations are not contemporaneous

Figure~\ref{fig:time_wise_correlation} summarizes time-wise correlations from
these five signals over the same time period, and for the same set of counties.
For each signal, we display the set of correlations that it achieves in
histogram form (more precisely, using a kernel density estimate). All signals
produce positive correlations in the majority of counties considered (with very
little mass in each estimated density being to the left of zero). The largest
correlations, in bulk, are achieved by the CHNG-COVID signal; the
CTIS-CLI-in-community signal is a close second, and the CHNG-CLI signal is
third. There are two noteworthy points:

@@

\item It is still quite impressive (and surprising) that the
  CTIS-CLI-in-community signal, based on people reporting on the symptoms of
  others around them, can achieve  nearly as strong time-wise correlations to
  confirmed cases as can a signal that is based on picking up the occurrence of
  a confirmed case passing through the outpatient system.
\end{itemize}
The Supplementary Information contains additional correlation analyses that
compare these COVID-related signals to COVID hospitalizations reported by the
Department of Health and Human Services. These show similar results,
illustrating that the signals are useful for tracking key health outcomes.

>>>>

Figure~\ref{fig:time_wise_correlation} summarizes time-wise correlations from
these five signals over the same time period, and for the same set of counties.
For each signal, we display the set of correlations that it achieves in
histogram form (more precisely, using a kernel density estimate). All signals
produce positive correlations in the majority of counties considered (with very
little mass in each estimated density being to the left of zero). The largest
correlations, in bulk, are achieved by the CHNG-COVID signal; the
CTIS-CLI-in-community signal is a close second, and the CHNG-CLI signal is
third. There are three noteworthy points:

@@

\item It is still quite impressive (and surprising) that the
  CTIS-CLI-in-community signal, based on people reporting on the symptoms of
  others around them, can achieve  nearly as strong time-wise correlations to
  confirmed cases as can a signal that is based on picking up the occurrence of
  a confirmed case passing through the outpatient system.

\item As we will discuss below in more detail, public health reporting is often
  subject to delays and backlogs that cause data to be reported with lag.
  Meanwhile, signals such as CTIS-CLI-in-community can be reported with as
  little as 1--2 days of lag. These high correlations hence indicate a high
  correlation with a case value that may have only been officially reported days
  after these signals.
\end{itemize}
The Supplementary Information contains additional correlation analyses that
compare these COVID-related signals to COVID hospitalizations reported by the
Department of Health and Human Services. These show similar results,
illustrating that the signals are useful for tracking key health outcomes.
